---
title: "Fancy Title"
header-includes:
  - \usepackage{graphicx}
  - \usepackage{amsmath}
  - \usepackage{float}
  - \usepackage{hyperref}
  - \usepackage{setspace}
  - \onehalfspacing
output: pdf_document
latex_engine: lualatex
geometry: margin = 3.5cm
bibliography: references.bib
---

```{r, eval = TRUE, echo = FALSE, include = FALSE, cache = TRUE}
# source("C:/Users/Julian/cms/bachelor-thesis_Winkel/impl/voiproduction.R")

```

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')
```
\pagenumbering{gobble}

<!-- \newcommand{\quantnet}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{C:/Users/Julian/cms/bachelor-thesis_Winkel/written/thesis/qletlogo.pdf}}\,} -->


\makeatletter
\renewcommand\paragraph{\@startsection{paragraph}{4}{\z@}%
            {-2.5ex\@plus -1ex \@minus -.25ex}%
            {1.25ex \@plus .25ex}%
            {\normalfont\normalsize\bfseries}}
\makeatother
\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{4}    

\bigskip

\begin{center}

Business Analytics and Data Science Group Project  

\medskip
submitted to  
\medskip



\textbf{First Prof} \linebreak
\textbf{Second Prof}  \linebreak


\medskip
Humboldt-Universit?t zu Berlin \linebreak     
School of Business and Economics  \linebreak
\medskip


Chair  \linebreak

by  \linebreak  

\textbf{Claudia Guenther, Phi Nguyen, Julian Winkel}  \linebreak  
Immatriculation Numbers \linebreak




\includegraphics[width=0.3\textwidth]{HU_Logo_small.png}

\medskip

Anything else we want to say

\medskip


Berlin, Date

\end{center}


\newpage
\pagenumbering{roman}



\begin{abstract}

\smallskip

Insert abstract here

\bigskip



\end{abstract}

\newpage

\listoftables

\newpage

\listoffigures

\newpage


\begin{Large}
\textbf{Abbreviations} \linebreak
\end{Large}

\begin{tabular}{ll}
\textbf{ANN} & Artificial Neural Network     \\
\textbf{LM} & Linear Model    \\

\end{tabular}


\newpage

\pagenumbering{arabic}

\tableofcontents

\newpage

\section{Introduction}


\newpage


\section{Previous Literature}
1 Page

Divide previous research in subsections that will be presented in the following.

This is how we cite @Badea_2014. The reference is automatically pasted in the according section.
You can also cite indirectly at the end of a sentence [@Badea_2014].
In this format, it is possible to insert pages, too [@Badea_2014, 10-14].


\clearpage
\newpage

\section{Methodoloy}
2 pages
\subsection{Predictive Analytics or other title}

\subsection{Ensemble Models}

\newpage


\clearpage

\newpage

\section{Data}
\subsection{Data sets}
The two data sets available to us contain a total of 150,000 order records from an online apparel retailer from a yearlong selling period. For 50,000 of these records it is unknown whether an ordered item has been sent back by the customer or not. This second data set is the subject of our binary predictions of customer’s returning behavior (return/not return). Both data sets include a total of 13 continuous and categorical variables.  These covariates give information on customer demographics (e.g. user state, date of birth, title), order details (e.g. order date, delivery date), and item characteristics (e.g. item size, price or color). To prepare the data sets for our analysis we apply a set of standard pre-processing actions. Following the careful inspection of each variable, we remove all implausible values (e.g. extreme outliers). Approximately 20% of all records have missing values in either the *delivery date* and *date of birth*. For bettter comprehensibility, we transform these variables *delivery time* and *age* respectively. Since *age* seems to be missing (completely) at random (MCAR) according to our data inspection, imputing it using mean substitution gives us an unbiased estimates [@schafer2002missing]^[Additionally, we carry out a Maximum Likelihood imputation of age in case the missing values are only missing at random (MAR), yielding the same model performance.].
Missing values in delivery time, caused by missing delivery dates, are clearly not missing not at random (MNAR) as they have a zero mean return rate and therefore are a perfect predictor. Possible reasons for this are manifold. Without knowing the process generating these MNAR values, we cannot find unbiased substitutes form them [@schafer2002missing, 171]. We adopt three single substitution methods, namely case dropping, mean and median imputation, and chose the latter one based on model performance. We standardize the continuous variables only after the feature creation step to maintain their interpretability. Likewise, we do not directly drop zero (almost) zero variance predictors (e.g. date of birth) since we use them for feature extraction.
\subsection{Feature creation and selection}

\newpage

\section{Model building}
\subsection{Experimental design}
\subsubsection{Baseline models}
\subsubsection{Candidate selection and combination}
\subsection{Performance Measurement}
- discuss AUC, accuracy, costs
- post-processing

\clearpage
\newpage

\section{Results}


\section{Conclusion}


\newpage

\section{References}


<div id="refs"></div>


\newpage

\begin{Large}
\textbf{Declaration of Authorship}
\end{Large}

\bigskip
\bigskip

TEXT

\bigskip
\bigskip

15.01.2018
