---
title: "Fancy Title"
header-includes:
  - \usepackage{graphicx}
  - \usepackage{amsmath}
  - \usepackage{float}
  - \usepackage{hyperref}
output: pdf_document
latex_engine: lualatex
geometry: margin = 4.5cm
bibliography: references.bib
---

```{r, eval = TRUE, echo = FALSE, include = FALSE, cache = TRUE} 
# source("C:/Users/Julian/cms/bachelor-thesis_Winkel/impl/voiproduction.R")

```

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')
```
\pagenumbering{gobble}

<!-- \newcommand{\quantnet}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{C:/Users/Julian/cms/bachelor-thesis_Winkel/written/thesis/qletlogo.pdf}}\,} -->


\makeatletter
\renewcommand\paragraph{\@startsection{paragraph}{4}{\z@}%
            {-2.5ex\@plus -1ex \@minus -.25ex}%
            {1.25ex \@plus .25ex}%
            {\normalfont\normalsize\bfseries}}
\makeatother
\setcounter{secnumdepth}{4} 
\setcounter{tocdepth}{4}    

\bigskip

\begin{center}

Business Analytics and Data Science Group Project  

\medskip
submitted to  
\medskip



\textbf{First Prof} \linebreak
\textbf{Second Prof}  \linebreak
 

\medskip
Humboldt-Universität zu Berlin \linebreak     
School of Business and Economics  \linebreak
\medskip


Chair  \linebreak 

by  \linebreak  

\textbf{Claudia Günther, Phi Nguyen, Julian Winkel}  \linebreak  
Immatriculation Numbers \linebreak




\includegraphics[width=0.3\textwidth]{HU_Logo_small.png}

\medskip

Anything else we want to say

\medskip


Berlin, Date 

\end{center}


\newpage
\pagenumbering{roman}



\begin{abstract}

\smallskip

Insert abstract here

\bigskip



\end{abstract}

\newpage

\listoftables

\newpage

\listoffigures

\newpage


\begin{Large}
\textbf{Abbreviations} \linebreak
\end{Large}

\begin{tabular}{ll}
\textbf{ANN} & Artificial Neural Network     \\
\textbf{LM} & Linear Model    \\
 
\end{tabular}


\newpage

\pagenumbering{arabic}

\tableofcontents

\newpage

\section{Introduction}


\newpage


\section{Previous Research}


\subsection{Overview}

Divide previous research in subsections that will be presented in the following.


\subsection{Research on ANN}

This is how we cite @Badea_2014. The reference is automatically pasted in the according section.
You can also cite indirectly at the end of a sentence [@Badea_2014].
In this format, it is possible to insert pages, too [@Badea_2014, 10-14].



\subsection{Research on ...}


\clearpage
\newpage

\section{Data}




\newpage



\clearpage

\newpage


\section{Descriptive Analysis}



\clearpage




\newpage




\subsection{Summary Statistics}




\newpage

\section{Model 1}

\subsection{Estimated Model 1}


\subsection{Model 1 Diagnosis}


\clearpage
\newpage



\section{Conclusion}


\newpage

\section{References}


<div id="refs"></div>


\newpage

\begin{Large}
\textbf{Declaration of Authorship} 
\end{Large}

\bigskip
\bigskip

TEXT

\bigskip
\bigskip

15.01.2018










